---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
    
---


## Loading and preprocessing the data
```{r}
unzip("activity.zip")
data <- read.csv("activity.csv",header = T)
```



## What is mean total number of steps taken per day?
```{r fig.path='figure/' }
library(data.table)
library(ggplot2)
data_dt <- as.data.table(data)
total_per_day <- data_dt[,.(total = sum(steps,na.rm = T)),by =date]
qplot(total_per_day$total,xlab = "Steps",ylab = "Count",binwidth = 500)


TotalMean <- mean(data_dt$steps,na.rm = T)
TotalMedian <- median(data_dt$steps,na.rm = T)


```
 Mean: `r TotalMean`
 Median: `r TotalMedian`




## What is the average daily activity pattern?
```{r fig.path='figure/' }
avg_per_interval <- data_dt[,.(avg_steps=mean(steps,na.rm = T)),by = interval]
ggplot(data = avg_per_interval,aes(x=interval,y=avg_steps))+
  geom_line() + 
  xlab("5-minute interval")+
  ylab("average number of steps taken")

max_interval <- avg_per_interval[which.max(avg_steps),interval]

```
`r max_interval` contains number of steps  across all the days
 


## Imputing missing values
```{r, warning=FALSE， fig.path='figure/' }
total_NAs <- data_dt[!complete.cases(data_dt),.N]

data_complete <- data_dt[which(!complete.cases(data_dt)),steps:=mean(data_dt$steps,na.rm = T)]

total_per_day <- data_complete[,.(total = sum(steps,na.rm = T)),by =date]
qplot(total_per_day$total,xlab = "Steps",ylab = "Count",binwidth = 500)

TotalMean <- mean(data_complete$steps,na.rm = T)
TotalMedian <- median(data_complete$steps,na.rm = T)


```
* Number of missing values `r total_NAs`
* Mean (Imputed): `r TotalMean`
* Median (Imputed):  `r TotalMedian`


## Are there differences in activity patterns between weekdays and weekends?


```{r,message=FALSE,warning=FALSE，fig.path='figure/' }
library(lubridate)
data_complete[,wdays := ifelse(wday(date)%in%c(1,7),"Weekend","weekday")]
data_complete$wdays <- as.factor(data_complete$wdays)
avg_per_interval <- data_complete[,.(avg = mean(steps)),by=.(interval,wdays)]

ggplot(data = avg_per_interval,aes(x=interval,y=avg)) + geom_line()+
  facet_grid(wdays~.)+ ylab("average steps")+xlab("interval")

```

